Optimizing Computational Graph Configurations for TPU Compilers with GNNs

### 2023-11-09 paper/main.tex
Update main.tex

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{url}
\usepackage{booktabs}
\usepackage{amsfonts}
\usepackage{nicefrac}
\usepackage{microtype}
\usepackage{lipsum}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{doi}
\usepackage[dvipsnames]{xcolor}
\usepackage[dvipsnames]{xcolor}
\usepackage{tablefootnote}
\usepackage{amssymb}

@@

To tackle the aforementioned challenges, Graph Segment Training (GST) was employed as illustrated in Fig. \ref{fig:main_schema}. This method involves dividing each large graph into smaller, controlled-size segments during the preprocessing phase. Throughout the training process, a random subset of segments at each step is selected, updating the model without utilizing the entire graph, i.e. $$\mathcal{G}^{(i)} = \bigoplus \mathcal{G}^{(i)}_{j}, \; \; \; \; \; j \in \mathcal{J} = \{1, ... , \frac{\mathcal{L}(\mathcal{G}^{(i)})}{\mathcal{K}}\}$$, where $\mathcal{K}$ is maximum allowed subgraph nodes count and $\mathcal{L}(\mathcal{G}^{(i)})$ is a count of nodes in graph $\mathcal{G}^{(i)}$ (see \cite{cao2023learning} for more details).

@@

>>>>

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{url}
\usepackage{booktabs}
\usepackage{amsfonts}
\usepackage{nicefrac}
\usepackage{microtype}
\usepackage{lipsum}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{doi}
\usepackage[dvipsnames]{xcolor}
\usepackage[dvipsnames]{xcolor}
\usepackage{tablefootnote}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

@@

To tackle the aforementioned challenges, Graph Segment Training (GST) was employed as illustrated in Fig. \ref{fig:main_schema}. This method involves dividing each large graph into smaller, controlled-size segments during the preprocessing phase. Throughout the training process, a random subset of segments at each step is selected, updating the model without utilizing the entire graph, i.e. $$\mathcal{G}^{(i)} = \bigoplus \mathcal{G}^{(i)}_{j}, \; \; \; \; \; j \in \mathcal{J} = \{1, ... , \frac{\mathcal{L}(\mathcal{G}^{(i)})}{\mathcal{K}}\},$$ where $\mathcal{K}$ is maximum allowed subgraph nodes count and $\mathcal{L}(\mathcal{G}^{(i)})$ is a count of nodes in graph $\mathcal{G}^{(i)}$ (see \cite{cao2023learning} for more details).

@@

The final prediction is the result of MLP layer applied to $\mathcal{G}^{(i)}_{j}$. The algorithm is written in List. \ref{alg:mainalgorithm}. In the experiments pairwise hinge loss was used.
\begin{algorithm}
\caption{GST TPU prediction algorithm}\label{alg:mainalgorithm}
\begin{algorithmic}[1]
\Procedure{GST\_TPU}{$\mathcal{G}^{(i)}, b$}\Comment{retrieve rank of given graph representation with backward on b parts}
\State $n \gets \lceil \frac{\mathcal{L}(\mathcal{G}^{(i)})}{\mathcal{K}} \rceil$
\State $\mathcal{Y} \gets RandSubset(\{1, ..., n\}, b)$\Comment{Sample min(b, n) items of set}
\State $E \gets  Zeroslike(emb)$\Comment{$emb$ is embedding dimension, this variable keeps final graph embedding}
\For{$j \in \{1, ... , n\}$}\Comment{For each graph part}
\State $\mathcal{G}^{(i)}_{j} \gets Slice(\mathcal{G}^{(i)}, (i-1)*\mathcal{K}, i*\mathcal{K})$\Comment{Subgraph is a node and edges slice}
\If{$j \in \mathcal{Y}$} \Comment{$\mathcal{M}$ is a model (GAT)}
\State $ E +=  \mathcal{M}(\mathcal{M}_1(opcodes \gets \mathcal{G}^{(i)}_{j}) + \mathcal{M}_2(configs \gets \mathcal{G}^{(i)}_{j}) + \mathcal{M}_3(nodes \gets \mathcal{G}^{(i)}_{j}))$
\Else
\State $ E +=  StopGrad(\mathcal{M} (\mathcal{M}_1(opcodes \gets \mathcal{G}^{(i)}_{j}) + \mathcal{M}_2(configs \gets \mathcal{G}^{(i)}_{j}) + \mathcal{M}_3(nodes \gets \mathcal{G}^{(i)}_{j})))$
\EndIf
\EndFor\label{euclidendwhile}
\State \textbf{return} $E$\Comment{The resulted embedding which may be used to train model}
\EndProcedure
\end{algorithmic}
\end{algorithm}
